Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-24 paper/paper.qmd
final paper updates

For the NRC index, @fig-sentiment-category further details the emotional nuances of SOC literature. The dominant emotional connotation in SOC literature's vocabulary is negative, standing at 16% to 22%. While the second highest percentage range belong to words with positive connotation, ranging from 11% to 17%. However, most of the other bars in the graph are occupied by words with negative-leaning emotions, such as sadness, fear, and anger. Sadness-related words, in particular, ranges the third highest, from 11% to 15%.

>>>>

For the NRC index, @fig-sentiment-category further details the emotional nuances of SOC literature. The dominant emotional connotation in SOC literature's vocabulary is negative, standing at 16% to 22%. While the second highest percentage range belongs to words with positive connotation, ranging from 11% to 17%. However, most of the other bars in the graph are occupied by words with negative-leaning emotions, such as sadness, fear, and anger. Sadness-related words, in particular, range the third highest, from 11% to 15%.
